|

### 2015-12-11 manuscript/manuscript_wtc3.Rmd
new methods

<!-- \ -->
<!-- Courtney E. Campany^1^, Belinda Medlyn^1^, Mark Tjoelker^1^, Susanne von Caemmerer^2^, Remko A. Duursma^1^. -->

<!-- \ -->
<!-- ^1^ Hawkesbury Institute for the Environment, Western Sydney University, Locked Bag 1797, Penrith, NSW, Australia -->

<!-- \ -->
<!-- ^2^ Plant Science Division, Research School of Biology, The Australian National University, Canberra, ACT, Australia -->

<!-- \ -->
<!-- *Corresponding author*: -->
<!-- Courtney Campany -->
<!-- E: courtneycampany@gmail.com -->

>>>>

\
Courtney E. Campany^1^, Belinda Medlyn^1^, Mark Tjoelker^1^, Susanne von Caemmerer^2^, Remko A. Duursma^1^.

\
^1^ Hawkesbury Institute for the Environment, Western Sydney University, Locked Bag 1797, Penrith, NSW, Australia

\
^2^ Plant Science Division, Research School of Biology, The Australian National University, Canberra, ACT, Australia

\
*Corresponding author*:
Courtney Campany
E: courtneycampany@gmail.com
